### 2016-01-29 AssignmentXI/Assignment10-Ditz_Schroeder-WS15-16.tex
aufgabe 3 ist fertig

% Definition des Headers
\usepackage{geometry}
\geometry{a4paper, top=3cm, left=3cm, right=3cm, bottom=3cm, headsep=0mm, footskip=0mm}
\renewcommand{\baselinestretch}{1.3}\normalsize

@@

\section{Theoretical Assignment - \textit{On distances}}
\subsection{title}

@@

\begin{thebibliography}{20}

\end{thebibliography}

>>>>

% Definition des Headers
\usepackage{geometry}
\geometry{a4paper, top=3cm, left=3cm, right=3cm, bottom=3cm, headsep=0mm, footskip=0mm}
\renewcommand{\baselinestretch}{1.3}\normalsize
\renewcommand{\thesubsection}{\thesection\alph{subsection}}

@@

\section{Theoretical Assignment - \textit{On distances}}
\subsection{}

@@

\begin{figure}[t]
 \centering
 \includegraphics[width=0.6\textwidth]{exec3bFigure.png}
 \caption{Behavior of observed distance $p$ and expected genetic distance $d$ of two non-saturated sequences. Both sequences are of length 200.}
 \label{fig:pdRelationship}
\end{figure}

There are different methods to estimate the (evolutionary) distance between two sequences. The easiest 
one is to simply calculate the Hamming distance. This is called the observed or $p$-distance. $p$-distance 
is just suitable for closely related species, since it is not able to detect superimposed mutations, i.e. 
mutations that happened at a position that was already mutated, previously. A correction for observed 
distance was formulated by Jukes and Cantor. The Jukes-Cantor transformation corrects the $p$-distance 
to take, among others, superimposed events into account. This correct distance is called the expected 
genetic distance $d$. An important note is that JC transformation does 
not work for sequences that are saturated w.r.t. each other. So Figure \ref{fig:pdRelationship} shows 
the relationship between $d$ and $p$ for non-saturated sequences of length 200. As one can see the 
observed distance $p$ is constantly underestimating the genetic distance for more distant sequences. 
Especially, if both sequences are close to be saturated, the difference between $d$ and $p$ shows 
that $p$ cannot give a reliable result. So for sequences/species that are evolutionary close to each 
other both measurements $d$ and $p$ give almost the same result. But the further away the last common 
ancestor of both sequences the larger is the difference between observed distance and expected genetic 
distance.

%\begin{thebibliography}{20}
%	
%\end{thebibliography}
